---
title: "Crossing structures data exploration"
output:
  pdf_document: default
  html_document: default
---

```{r, echo=FALSE, include=FALSE}

#Script to look at outliers, zeros and autocorrelation

rm(list = ls())

#-----------------Set working directory--------------------
setwd("/Users/hannahedwards/Documents/Alberta Parks/Crossing-structures/data/")
#setwd("/Users/eleonorelebeuf-taylor/Google Drive/Kananaskis crossing structures/")

#----------------Load libraries.-------------
library(MCMCglmm)
library(lmtest)
library(vioplot)
library(zoo)
library(circular)
library(tinytex)
library(regclass)
library(knitr)
library(xts)

#-----------------Load data--------------------
#ungulates.hourly <- read.csv("ungulates hourly.csv")
#ungulates.monthly <- read.csv("ungulates monthly.csv")
#ungulates.annual <- read.csv("ungulates annual.csv")

#carnivores.hourly <- read.csv("carnivores hourly.csv")
#carnivores.monthly <- read.csv("carnivores monthly.csv")
#carnivores.annual <- read.csv("carnivores annual.csv")

#Split by crossing structure type
ungulates.hourly <- read.csv("ungulates hourly.csv")
ungulates.hourly.under<-subset(ungulates.hourly, ungulates.hourly$Underpass.type != "Jumpout")
ungulates.hourly.jump<-subset(ungulates.hourly, ungulates.hourly$Underpass.type != "Underpass")
ungulates.monthly <- read.csv("ungulates monthly.csv")
ungulates.monthly.under<-subset(ungulates.monthly, ungulates.monthly$Underpass.type != "Jumpout")
ungulates.monthly.jump<-subset(ungulates.monthly, ungulates.monthly$Underpass.type != "Underpass")
ungulates.annual <- read.csv("ungulates annual.csv")
ungulates.annual.under<-subset(ungulates.annual, ungulates.annual$Underpass.type != "Jumpout")
ungulates.annual.jump<-subset(ungulates.annual, ungulates.annual$Underpass.type != "Underpass")

carnivores.hourly <- read.csv("carnivores hourly.csv")
carnivores.hourly.under<-subset(carnivores.hourly, carnivores.hourly$Underpass.type != "Jumpout")
carnivores.hourly.jump<-subset(carnivores.hourly, carnivores.hourly$Underpass.type != "Underpass")
carnivores.monthly <- read.csv("carnivores monthly.csv")
carnivores.monthly.under<-subset(carnivores.monthly, carnivores.monthly$Underpass.type != "Jumpout")
carnivores.monthly.jump<-subset(carnivores.monthly, carnivores.monthly$Underpass.type != "Underpass")
carnivores.annual <- read.csv("carnivores annual.csv")
carnivores.annual.under<-subset(carnivores.annual, carnivores.annual$Underpass.type != "Jumpout")
carnivores.annual.jump<-subset(carnivores.annual, carnivores.annual$Underpass.type != "Underpass")
```

#-------------------------------------------Look for outliers in guild count-----------------------------------------------

```{r, eval=TRUE, echo=FALSE}
summary(carnivores.annual$Total)
hist(carnivores.annual$Total, xlab="Total annual carnivore count per crossing structure",
      ylim=c(0,50), main="Figure 1")

summary(carnivores.monthly$Total)
hist(carnivores.monthly$Total, xlab="Total monthly carnivore count per crossing structure",
     ylim=c(0,40), main="Figure 2")

summary(carnivores.hourly$Total)
hist(carnivores.hourly$Total, xlab="Total hourly carnivore count per crossing structure",
     ylim=c(0,100), main="Figure 3")

summary(ungulates.annual$Total)
hist(ungulates.annual$Total, xlab="Total annual ungulate count per crossing structure",
     ylim=c(0,50), main="Figure 4")

summary(ungulates.monthly$Total)
hist(ungulates.monthly$Total, xlab="Total monthly ungulate count per crossing structure",
     ylim=c(0,50), main="Figure 5")

summary(ungulates.hourly$Total)
hist(ungulates.hourly$Total, xlab="Total hourly ungulate count per crossing structure",
     ylim=c(0,100), main="Figure 6")

```
#----------------------------------------------Look for zeros in the data--------------------------------------------------

#Proportion of zeros in the carnivore dataset
```{r, eval=TRUE, echo=FALSE}
Annual_carnivore_count_underpass<-sum(carnivores.annual.under$Total == 0)/length(carnivores.annual.under$Total) 
#Annual carnivore count for jumpouts
Annual_carnivore_count_jumpout<-sum(carnivores.annual.jump$Total == 0)/length(carnivores.annual.jump$Total)  
#Monthly carnivore count for underpasses
Monthly_carnivore_count_underpass<-sum(carnivores.monthly.under$Total == 0)/length(carnivores.monthly.under$Total)  
#Monthly carnivore count for jumpouts
Monthly_carnivore_count_jumpout<-sum(carnivores.monthly.jump$Total == 0)/length(carnivores.monthly.jump$Total) 
#Hourly carnivore count for underpasses
Hourly_carnivore_count_underpass<-sum(carnivores.hourly.under$Total == 0)/length(carnivores.hourly.under$Total)  
#Hourly carnivore count for jumpouts
Hourly_carnivore_count_jumpout<-sum(carnivores.hourly.jump$Total == 0)/length(carnivores.hourly.jump$Total)  

Table1<-rbind(Annual_carnivore_count_jumpout, Annual_carnivore_count_underpass, Monthly_carnivore_count_jumpout, Monthly_carnivore_count_underpass, 
      Hourly_carnivore_count_jumpout, Hourly_carnivore_count_underpass)
Table1<-round(Table1, digits=2)
colnames(Table1)[1]  <- "Proportion of zeros"
kable(Table1, caption=".")

```

#Proportion of zeros in the ungulate dataset
```{r, eval=TRUE, echo=FALSE}

Annual_ungulate_count_underpass<-sum(ungulates.annual.under$Total == 0)/length(ungulates.annual.under$Total)
#Annual ungulate count for jumpouts
Annual_ungulate_count_jumpout<-sum(ungulates.annual.jump$Total == 0)/length(ungulates.annual.jump$Total) 
#Monthly ungulate count for underpasses
Monthly_ungulate_count_underpass<-sum(ungulates.monthly.under$Total == 0)/length(ungulates.monthly.under$Total) 
#Monthly ungulate count for jumpouts
Monthly_ungulate_count_jumpout<-sum(ungulates.monthly.jump$Total == 0)/length(ungulates.monthly.jump$Total)  
#Hourly ungulate count for underpasses
Hourly_ungulate_count_underpass<-sum(ungulates.hourly.under$Total == 0)/length(ungulates.hourly.under$Total)  
#Hourly ungulate count for jumpouts
Hourly_ungulate_count_jumpout<-sum(ungulates.hourly.jump$Total == 0)/length(ungulates.hourly.jump$Total)  

Table2<-rbind(Annual_ungulate_count_jumpout, Annual_ungulate_count_underpass, Monthly_ungulate_count_jumpout, Monthly_ungulate_count_underpass, 
      Hourly_ungulate_count_jumpout, Hourly_ungulate_count_underpass)
Table2<-round(Table2, digits=2)
colnames(Table2)[1]  <- "Proportion of zeros"
kable(Table2, caption=".")

```

#--------------------------------------------Check for autocorrelation-----------------------------------------------------
# Run Box-Pierce and Ljung-Box test on the raw data
# Build a model of the mean (lm(count~1)) and run Durbin Watson test to test residuals

#Annual carnivore count for jumpouts

```{r, eval=TRUE, echo=FALSE}
car.ann.count.jump<-carnivores.annual.jump$Total
car.ann.count.jump.mod <- lm(car.ann.count.jump ~ 1)
dwtest(car.ann.count.jump.mod) #DW test (tests the residuals)-not autocorrelated
Box.test(car.ann.count.jump, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(car.ann.count.jump, lag = 1, type = c("Ljung-Box"), fitdf = 0)
acf(car.ann.count.jump, xlab="Total carnivore annual count for jumpouts",
    main="Figure 7") #plot acf
carnivores.annual.jump <- carnivores.annual.jump[order(carnivores.annual.jump$Year),] 
plot(x=carnivores.annual.jump$Year, y=carnivores.annual.jump$Total,
     xlab="Year", 
     ylab="Total carnivore annual count for underpasses", type="l",
     main="Figure 8")
var(car.ann.count.jump)
mean(car.ann.count.jump)
```

#Annual carnivore count for underpasses

```{r, eval=TRUE, echo=FALSE}
car.ann.count.under<-carnivores.annual.under$Total
car.ann.count.under.mod <- lm(car.ann.count.under ~ 1)
dwtest(car.ann.count.under.mod) #not autocorrelated
Box.test(car.ann.count.under, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(car.ann.count.under, lag = 1, type = c("Ljung-Box"), fitdf = 0)
acf(car.ann.count.under, xlab="Total carnivore annual count for underpasses",
    main="Figure 9")
carnivores.annual.under <- carnivores.annual.under[order(carnivores.annual.under$Year),] 
plot(x=carnivores.annual.under$Year, y=carnivores.annual.under$Total,
     xlab="Year",
     ylab="Total carnivore annual count for underpasses", type="l",
     main="Figure 10")
var(car.ann.count.under)
mean(car.ann.count.under)
```

#Monthly carnivore count for jumpouts

```{r, eval=TRUE, echo=FALSE}
car.mon.count.jump<-carnivores.monthly.jump$Total
car.mon.count.jump.mod <- lm(car.mon.count.jump ~ 1)
dwtest(car.mon.count.jump.mod) #DW test (tests the residuals)-not autocorrelated
Box.test(car.mon.count.jump, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(car.mon.count.jump, lag = 1, type = c("Ljung-Box"), fitdf = 0)
acf(car.mon.count.jump, xlab="Total carnivore monthly count for jumpouts",
    main="Figure 11") #plot acf
carnivores.monthly.jump <- carnivores.monthly.jump[order(carnivores.monthly.jump$Month),] 
plot(x=carnivores.monthly.jump$Month, y=carnivores.monthly.jump$Total,
     xlab="Month",
     ylab="Total carnivore monthly count for jumpouts", type="l",
     main="Figure 12")
var(car.mon.count.jump)
mean(car.mon.count.jump)
```

#Monthly carnivore count for underpasses

```{r, eval=TRUE, echo=FALSE}
car.mon.count.under<-carnivores.monthly.under$Total
car.mon.count.under.mod <- lm(car.mon.count.under ~ 1)
dwtest(car.mon.count.under.mod) #DW test (tests the residuals)-not autocorrelated
Box.test(car.mon.count.under, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(car.mon.count.under, lag = 1, type = c("Ljung-Box"), fitdf = 0)
acf(car.mon.count.under, xlab="Total carnivore monthly count for underpasses",
    main="Figure 13") #plot acf
carnivores.monthly.under <- carnivores.monthly.under[order(carnivores.monthly.under$Month),] 
plot(x=carnivores.monthly.under$Month, y=carnivores.monthly.under$Total,
     xlab="Month",
     ylab="Total carnivore monthly count for underpasses", type="l",
     main="Figure 14")
var(car.mon.count.under)
mean(car.mon.count.under)
```
#Hourly carnivore count for jumpouts

```{r, eval=TRUE, echo=FALSE}
car.hou.count.jump<-carnivores.hourly.jump$Total
car.hou.count.jump.mod <- lm(car.hou.count.jump ~ 1)
dwtest(car.hou.count.jump.mod) #DW test (tests the residuals)-not autocorrelated
Box.test(car.hou.count.jump, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(car.hou.count.jump, lag = 1, type = c("Ljung-Box"), fitdf = 0)
acf(car.hou.count.jump, xlab="Total carnivore hourly count for jumpouts",
    main="Figure 15") #plot acf
carnivores.hourly.jump <- carnivores.hourly.jump[order(carnivores.hourly.jump$HourEnding),] 
plot(x=carnivores.hourly.jump$HourEnding, y=carnivores.hourly.jump$Total,
     xlab="Hour",
     ylab="Total carnivore hourly count for jumpouts", type="l",
     main="Figure 16")
var(car.hou.count.jump)
mean(car.hou.count.jump)
```

#Hourly carnivore count for underpasses

```{r, eval=TRUE, echo=FALSE}
car.hou.count.under<-carnivores.hourly.under$Total
car.hou.count.under.mod <- lm(car.hou.count.under ~ 1)
dwtest(car.hou.count.under.mod) #DW test (tests the residuals)-not autocorrelated
Box.test(car.hou.count.under, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(car.hou.count.under, lag = 1, type = c("Ljung-Box"), fitdf = 0)
acf(car.hou.count.under, xlab="Total carnivore hourly count for underpasses",
    main="Figure 17") #plot acf
carnivores.hourly.under <- carnivores.hourly.under[order(carnivores.hourly.under$HourEnding),] 
plot(x=carnivores.hourly.under$HourEnding, y=carnivores.hourly.under$Total,
     xlab="Hour",
     ylab="Total carnivore hourly count for underpasses", type="l",
     main="Figure 18")
var(car.hou.count.under)
mean(car.hou.count.under)
```

#Annual ungulate count for jumpouts

```{r, eval=TRUE, echo=FALSE}
ung.ann.count.jump<-ungulates.annual.jump$Total
ung.ann.count.jump.mod <- lm(ung.ann.count.jump ~ 1)
dwtest(ung.ann.count.jump.mod) #DW test (tests the residuals)-not autocorrelated
Box.test(ung.ann.count.jump, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(ung.ann.count.jump, lag = 1, type = c("Ljung-Box"), fitdf = 0)
acf(ung.ann.count.jump, xlab="Total ungulates annual count for jumpouts",
    main="Figure 19") #plot acf
ungulates.annual.jump <- ungulates.annual.jump[order(ungulates.annual.jump$Year),] 
plot(x=ungulates.annual.jump$Year, y=ungulates.annual.jump$Total,
     xlab="Year",
     ylab="Total ungulates annual count for jumpouts", type="l",
     main="Figure 20")
var(ung.ann.count.jump)
mean(ung.ann.count.jump)
```

#Annual ungulate count for underpasses

```{r, eval=TRUE, echo=FALSE}
ung.ann.count.under<-ungulates.annual.under$Total
ung.ann.count.under.mod <- lm(ung.ann.count.under ~ 1)
dwtest(ung.ann.count.under.mod) #DW test (tests the residuals)-not autocorrelated
Box.test(ung.ann.count.under, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(ung.ann.count.under, lag = 1, type = c("Ljung-Box"), fitdf = 0)
acf(ung.ann.count.under, xlab="Total ungulates annual count for underpasses",
    main="Figure 21") #plot acf
ungulates.annual.under <- ungulates.annual.under[order(ungulates.annual.under$Year),] 
plot(x=ungulates.annual.under$Year, y=ungulates.annual.under$Total,
     xlab="Year",
     ylab="Total ungulates annual count for underpasses", type="l",
     main="Figure 22")
var(ung.ann.count.under)
mean(ung.ann.count.under)
```

#Monthly ungulate count for jumpouts

```{r, eval=TRUE, echo=FALSE}
ung.mon.count.jump<-ungulates.monthly.jump$Total
ung.mon.count.jump.mod <- lm(ung.mon.count.jump ~ 1)
dwtest(ung.mon.count.jump.mod) #DW test (tests the residuals)-not autocorrelated
Box.test(ung.mon.count.jump, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(ung.mon.count.jump, lag = 1, type = c("Ljung-Box"), fitdf = 0)
acf(ung.mon.count.jump, xlab="Total ungulates monthly count for jumpouts",
    main="Figure 23") #plot acf
ungulates.monthly.jump <- ungulates.monthly.jump[order(ungulates.monthly.jump$Month),] 
plot(x=ungulates.monthly.jump$Month, y=ungulates.monthly.jump$Total,
     xlab="Month",
     ylab="Total ungulates monthly count for jumpouts", type="l",
     main="Figure 24")
var(ung.mon.count.jump)
mean(ung.mon.count.jump)
```

#Monthly ungulate count for underpasses

```{r, eval=TRUE, echo=FALSE}
ung.mon.count.under<-ungulates.monthly.under$Total
ung.mon.count.under.mod <- lm(ung.mon.count.under ~ 1)
dwtest(ung.mon.count.under.mod) #DW test (tests the residuals)-not autocorrelated
Box.test(ung.mon.count.under, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(ung.mon.count.under, lag = 1, type = c("Ljung-Box"), fitdf = 0)
acf(ung.mon.count.under, xlab="Total ungulates monthly count for underpasses",
    main="Figure 25") #plot acf
ungulates.monthly.under <- ungulates.monthly.under[order(ungulates.monthly.under$Month),] 
plot(x=ungulates.monthly.under$Month, y=ungulates.monthly.under$Total,
     xlab="Month",
     ylab="Total ungulates monthly count for underpasses", type="l",
     main="Figure 26")
var(ung.mon.count.under)
mean(ung.mon.count.under)
```

#Hourly ungulate count for jumpouts

```{r, eval=TRUE, echo=FALSE}
ung.hou.count.jump<-ungulates.hourly.jump$Total
ung.hou.count.jump.mod <- lm(ung.hou.count.jump ~ 1)
dwtest(ung.hou.count.jump.mod) #DW test (tests the residuals)-not autocorrelated
Box.test(ung.hou.count.jump, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(ung.hou.count.jump, lag = 1, type = c("Ljung-Box"), fitdf = 0)
acf(ung.hou.count.jump, xlab="Total ungulates hourly count for jumpouts",
    main="Figure 27") #plot acf
ungulates.hourly.jump <- ungulates.hourly.jump[order(ungulates.hourly.jump$HourEnding),] 
plot(x=ungulates.hourly.jump$HourEnding, y=ungulates.hourly.jump$Total,
     xlab="Hour",
     ylab="Total ungulates hourly count for jumpouts", type="l",
     main="Figure 28")
var(ung.hou.count.jump)
mean(ung.hou.count.jump)
```

#Hourly ungulate count for underpasses

```{r, eval=TRUE, echo=FALSE}
ung.hou.count.under<-ungulates.hourly.under$Total
ung.hou.count.under.mod <- lm(ung.hou.count.under ~ 1)
dwtest(ung.hou.count.under.mod) #DW test (tests the residuals)-not autocorrelated
Box.test(ung.hou.count.under, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(ung.hou.count.under, lag = 1, type = c("Ljung-Box"), fitdf = 0)
acf(ung.hou.count.under, xlab="Total ungulates hourly count for underpasses",
    main="Figure 29") #plot acf
ungulates.hourly.under <- ungulates.hourly.under[order(ungulates.hourly.under$HourEnding),] 
plot(x=ungulates.hourly.under$HourEnding, y=ungulates.hourly.under$Total,
     xlab="Hour",
     ylab="Total ungulates hourly count for underpasses", type="l",
     main="Figure 30")
var(ung.hou.count.under)
mean(ung.hou.count.under)
```

#--------------------------------------------------------Violin plots------------------------------------------------------

```{r, echo=FALSE}
car.ann.count<-carnivores.annual$Total
ung.ann.count<-ungulates.annual$Total
car.mon.count<-carnivores.monthly$Total
ung.mon.count<-ungulates.monthly$Total
car.hou.count<-carnivores.hourly$Total
ung.hou.count<-ungulates.hourly$Total
```

```{r, eval=TRUE, echo=FALSE}
annual.counts<-cbind(car.ann.count,ung.ann.count)
month.counts<-cbind(car.mon.count,ung.mon.count)
#Make the hour counts the same length by adding NAs to carnivore vector
n<-max(length(car.hou.count),length(ung.hou.count))
length(car.hou.count)<-n
hour.counts<-cbind(car.hou.count,ung.hou.count)

vioplot(annual.counts, main="Figure 31")
vioplot(month.counts, main="Figure 32")
vioplot(hour.counts, main="Figure 33")
```

#--------------------------------------Look at whether there is circularity in the dataset---------------------------------

```{r, echo=FALSE}
#Setup the data differently, get frequencies of count for hour/month/year
newdata<-read.csv("/Users/hannahedwards/Documents/Alberta Parks/Crossing-structures/data/newdata.csv")
#Split by species and then crossing structure
ungulates.under<-subset(newdata, newdata$Species.grouped == "Ungulates" &
                                 newdata$Underpass.type == "Underpass")
ungulates.jump<-subset(newdata, newdata$Species.grouped == "Ungulates" &
                                 newdata$Underpass.type == "Jumpout")
carnivores.under<-subset(newdata, newdata$Species.grouped == "Carnivores" &
                                 newdata$Underpass.type == "Underpass")
carnivores.jump<-subset(newdata, newdata$Species.grouped == "Carnivores" &
                          newdata$Underpass.type == "Jumpout")
carnivores<-subset(newdata, newdata$Species.grouped == "Carnivores")
Bobcat<-subset(newdata, newdata$Species == "Bobcat")
Cougar<-subset(newdata, newdata$Species == "Cougar")
Coyote<-subset(newdata, newdata$Species == "Coyote")
GrizzlyBear<-subset(newdata, newdata$Species == "Grizzly Bear")
Lynx<-subset(newdata, newdata$Species == "Lynx")
Marten<-subset(newdata, newdata$Species == "Marten")
RedFox<-subset(newdata, newdata$Species == "Red Fox")
StripedSkunk<-subset(newdata, newdata$Species == "Striped Skunk")
UnknownBear<-subset(newdata, newdata$Species == "Unknown Bear")
Wolf<-subset(newdata, newdata$Species == "Wolf")
Wolverine<-subset(newdata, newdata$Species == "Wolverine")
BlackBear<-subset(newdata, newdata$Species == "Black Bear")
```

#Ungulate and carnivore hours of activity

```{r, eval=TRUE, echo=FALSE}
#Make data circular with hourending
#Vector
unghour<-ungulates.under$HourEnding
carhour<-carnivores.under$HourEnding
unghourc <- circular(unghour, units="hours", template="clock24")
carhourc <- circular(carhour, units="hours", template="clock24")
#the radius of a segment is taken to be the square root of the relative frequency
```
```{r, echo=FALSE, fig.show='hide'}
plot(unghourc)
```
```{r, eval=TRUE, echo=FALSE}
a<-rose.diag(unghourc, bins=24, col="darkgrey", cex=1.5, prop=1.3, add=FALSE,
             xlab="Ungulate hour frequency", main="Figure 34")
```
```{r, echo=FALSE, fig.show='hide'}
plot(carhourc)
```
```{r, eval=TRUE, echo=FALSE}
b<-rose.diag(carhourc, bins=24, col="darkgrey", cex=1.5, prop=1.3, add=FALSE,
             xlab="Carnivore hour frequency", main="Figure 35")
```

#Ungulate and carnivore months of activity

```{r, eval=TRUE, echo=FALSE}
#Make data circular with Month
#Vector
ungmon<-ungulates.under$Month
carmon<-carnivores.under$Month
ungmonc <- circular(ungmon, units="hours", template="clock12")
carmonc <- circular(carmon, units="hours", template="clock12")
#the radius of a segment is taken to be the square root of the relative frequency
```
```{r, echo=FALSE, fig.show='hide'}
plot(ungmonc)
```
```{r, eval=TRUE, echo=FALSE}
c<-rose.diag(ungmonc, bins=12, col="darkgrey", cex=1.5, prop=1.3, add=FALSE,
             xlab="Ungulate month frequency", main="Figure 36")
```
```{r, echo=FALSE, fig.show='hide'}
plot(carmonc)
```
```{r, eval=TRUE, echo=FALSE}
d<-rose.diag(carmonc, bins=12, col="darkgrey", cex=1.5, prop=1.3, add=FALSE,
             xlab="Carnivore month frequency", main="Figure 37")
```

#Carnivores hours of activity separated by species

```{r, eval=TRUE, echo=FALSE}
#Make data circular with hour for each carnivore species
carnivores$Species<-as.factor(carnivores$Species)
summary(carnivores$Species)

#Bobcat
Bobcathou<-Bobcat$HourEnding
Bobcathouc <- circular(Bobcathou, units="hours", template="clock24")
```
```{r, echo=FALSE, fig.show='hide'}
plot(Bobcathouc)
```
```{r, eval=TRUE, echo=FALSE}
c<-rose.diag(Bobcathouc, bins=24, col="darkgrey", cex=1.5, prop=1.3, add=FALSE,
             xlab="Bobcat hour frequency", main="Figure 38")
```
```{r, eval=TRUE, echo=FALSE}
#Coyote
Coyotehou<-Coyote$HourEnding
Coyotehouc <- circular(Coyotehou, units="hours", template="clock24")
```
```{r, echo=FALSE, fig.show='hide'}
plot(Coyotehouc)
```
```{r, eval=TRUE, echo=FALSE}
c<-rose.diag(Coyotehouc, bins=24, col="darkgrey", cex=1.5, prop=1.3, add=FALSE,
             xlab="Coyote hour frequency", main="Figure 39")
```
```{r, eval=TRUE, echo=FALSE}
#Cougar
Cougarhou<-Cougar$HourEnding
Cougarhouc <- circular(Cougarhou, units="hours", template="clock24")
```
```{r, echo=FALSE, fig.show='hide'}
plot(Cougarhouc)
```
```{r, eval=TRUE, echo=FALSE}
c<-rose.diag(Cougarhouc, bins=24, col="darkgrey", cex=1.5, prop=1.3, add=FALSE,
             xlab="Cougar hour frequency", main="Figure 40")
```
```{r, eval=TRUE, echo=FALSE}
#Grizzly Bear
GrizzlyBearhou<-GrizzlyBear$HourEnding
GrizzlyBearhouc <- circular(GrizzlyBearhou, units="hours", template="clock24")
```
```{r, echo=FALSE, fig.show='hide'}
plot(GrizzlyBearhouc)
```
```{r, eval=TRUE, echo=FALSE}
c<-rose.diag(GrizzlyBearhouc, bins=24, col="darkgrey", cex=1.5, prop=1.3, add=FALSE,
             xlab="Grizzly Bear hour frequency", main="Figure 41")
```
```{r, eval=TRUE, echo=FALSE}
#Lynx
Lynxhou<-Lynx$HourEnding
Lynxhouc <- circular(Lynxhou, units="hours", template="clock24")
```
```{r, echo=FALSE, fig.show='hide'}
plot(Lynxhouc)
```
```{r, eval=TRUE, echo=FALSE}
c<-rose.diag(Lynxhouc, bins=24, col="darkgrey", cex=1.5, prop=1.3, add=FALSE,
             xlab="Lynx hour frequency", main="Figure 42")
```
```{r, eval=TRUE, echo=FALSE}
#Marten
Martenhou<-Marten$HourEnding
Martenhouc <- circular(Martenhou, units="hours", template="clock24")
```
```{r, echo=FALSE, fig.show='hide'}
plot(Martenhouc)
```
```{r, eval=TRUE, echo=FALSE}
c<-rose.diag(Martenhouc, bins=24, col="darkgrey", cex=1.5, prop=1.3, add=FALSE,
             xlab="Pine Marten hour frequency", main="Figure 43")
```
```{r, eval=TRUE, echo=FALSE}
#RedFox
RedFoxhou<-RedFox$HourEnding
RedFoxhouc <- circular(RedFoxhou, units="hours", template="clock24")
```
```{r, echo=FALSE, fig.show='hide'}
plot(RedFoxhouc)
```
```{r, eval=TRUE, echo=FALSE}
c<-rose.diag(RedFoxhouc, bins=24, col="darkgrey", cex=1.5, prop=1.3, add=FALSE,
             xlab="Red Fox hour frequency", main="Figure 44")
```
```{r, eval=TRUE, echo=FALSE}
#StripedSkunk
StripedSkunkhou<-StripedSkunk$HourEnding
StripedSkunkhouc <- circular(StripedSkunkhou, units="hours", template="clock24")
```
```{r, echo=FALSE, fig.show='hide'}
plot(StripedSkunkhouc)
```
```{r, eval=TRUE, echo=FALSE}
c<-rose.diag(StripedSkunkhouc, bins=24, col="darkgrey", cex=1.5, prop=1.3, add=FALSE,
             xlab="Striped Skunk hour frequency", main="Figure 45")
```
```{r, eval=TRUE, echo=FALSE}
#UnknownBear
UnknownBearhou<-UnknownBear$HourEnding
UnknownBearhouc <- circular(UnknownBearhou, units="hours", template="clock24")
```
```{r, echo=FALSE, fig.show='hide'}
plot(UnknownBearhouc)
```
```{r, eval=TRUE, echo=FALSE}
c<-rose.diag(UnknownBearhouc, bins=24, col="darkgrey", cex=1.5, prop=1.3, add=FALSE,
             xlab="Unknown Bear hour frequency", main="Figure 46")
```
```{r, eval=TRUE, echo=FALSE}
#Wolf
Wolfhou<-Wolf$HourEnding
Wolfhouc <- circular(Wolfhou, units="hours", template="clock24")
```
```{r, echo=FALSE, fig.show='hide'}
plot(Wolfhouc)
```
```{r, eval=TRUE, echo=FALSE}
c<-rose.diag(Wolfhouc, bins=24, col="darkgrey", cex=1.5, prop=1.3, add=FALSE,
             xlab="Wolf hour frequency", main="Figure 47")
```
```{r, eval=TRUE, echo=FALSE}
#Wolverine
Wolverinehou<-Wolverine$HourEnding
Wolverinehouc <- circular(Wolverinehou, units="hours", template="clock24")
```
```{r, echo=FALSE, fig.show='hide'}
plot(Wolverinehouc)
```
```{r, eval=TRUE, echo=FALSE}
c<-rose.diag(Wolverinehouc, bins=24, col="darkgrey", cex=1.5, prop=1.3, add=FALSE,
             xlab="Wolverine hour frequency", main="Figure 48")
```
```{r, eval=TRUE, echo=FALSE}
#Black bear
BlackBearhou<-BlackBear$HourEnding
BlackBearhouc <- circular(BlackBearhou, units="hours", template="clock24")
```
```{r, echo=FALSE, fig.show='hide'}
plot(BlackBearhouc)
```
```{r, eval=TRUE, echo=FALSE}
c<-rose.diag(BlackBearhouc, bins=24, col="darkgrey", cex=1.5, prop=1.3, add=FALSE,
             xlab="Black Bear hour frequency", main="Figure 48")
```