---
title: "Crossing structures data exploration"

output: html_document
---

```{r, echo=FALSE, include=FALSE}

#Script to look at outliers, zeros and autocorrelation

rm(list = ls())

#-----------------Set working directory--------------------
setwd("/Users/hannahedwards/Documents/Alberta Parks/Crossing-structures/data/")
#setwd("/Users/eleonorelebeuf-taylor/Google Drive/Kananaskis crossing structures/")

#----------------Load libraries.-------------
library(MCMCglmm)
library(lmtest)
library(vioplot)
library(zoo)
library(circular)

#-----------------Load data--------------------
#ungulates.hourly <- read.csv("ungulates hourly.csv")
#ungulates.monthly <- read.csv("ungulates monthly.csv")
#ungulates.annual <- read.csv("ungulates annual.csv")

#carnivores.hourly <- read.csv("carnivores hourly.csv")
#carnivores.monthly <- read.csv("carnivores monthly.csv")
#carnivores.annual <- read.csv("carnivores annual.csv")

#Split by crossing structure type
ungulates.hourly <- read.csv("ungulates hourly.csv")
ungulates.hourly.under<-subset(ungulates.hourly, ungulates.hourly$Underpass.type != "Jumpout")
ungulates.hourly.jump<-subset(ungulates.hourly, ungulates.hourly$Underpass.type != "Underpass")
ungulates.monthly <- read.csv("ungulates monthly.csv")
ungulates.monthly.under<-subset(ungulates.monthly, ungulates.monthly$Underpass.type != "Jumpout")
ungulates.monthly.jump<-subset(ungulates.monthly, ungulates.monthly$Underpass.type != "Underpass")
ungulates.annual <- read.csv("ungulates annual.csv")
ungulates.annual.under<-subset(ungulates.annual, ungulates.annual$Underpass.type != "Jumpout")
ungulates.annual.jump<-subset(ungulates.annual, ungulates.annual$Underpass.type != "Underpass")

carnivores.hourly <- read.csv("carnivores hourly.csv")
carnivores.hourly.under<-subset(carnivores.hourly, carnivores.hourly$Underpass.type != "Jumpout")
carnivores.hourly.jump<-subset(carnivores.hourly, carnivores.hourly$Underpass.type != "Underpass")
carnivores.monthly <- read.csv("carnivores monthly.csv")
carnivores.monthly.under<-subset(carnivores.monthly, carnivores.monthly$Underpass.type != "Jumpout")
carnivores.monthly.jump<-subset(carnivores.monthly, carnivores.monthly$Underpass.type != "Underpass")
carnivores.annual <- read.csv("carnivores annual.csv")
carnivores.annual.under<-subset(carnivores.annual, carnivores.annual$Underpass.type != "Jumpout")
carnivores.annual.jump<-subset(carnivores.annual, carnivores.annual$Underpass.type != "Underpass")
```

#------------------------Look for outliers in guild count----------------------------

```{r, eval=TRUE, echo=FALSE}
summary(carnivores.annual$Total)
hist(carnivores.annual$Total, xlab="Total annual carnivore count per crossing structure",
     main=NULL, ylim=c(0,50))

summary(carnivores.monthly$Total)
hist(carnivores.monthly$Total, xlab="Total monthly carnivore count per crossing structure",
     main=NULL, ylim=c(0,40))

summary(carnivores.hourly$Total)
hist(carnivores.hourly$Total, xlab="Total hourly carnivore count per crossing structure",
     main=NULL, ylim=c(0,100))

summary(ungulates.annual$Total)
hist(ungulates.annual$Total, xlab="Total annual ungulate count per crossing structure",
     main=NULL, ylim=c(0,50))

summary(ungulates.monthly$Total)
hist(ungulates.monthly$Total, xlab="Total monthly ungulate count per crossing structure",
     main=NULL, ylim=c(0,50))

summary(ungulates.hourly$Total)
hist(ungulates.hourly$Total, xlab="Total hourly ungulate count per crossing structure",
     main=NULL, ylim=c(0,100))

```

#----------------------------Check for autocorrelation--------------------------
```{r, eval=TRUE, echo=FALSE}
#Annual carnivore count
#build a model of the mean 
car.ann.count.jump<-carnivores.annual.jump$Total
car.ann.count.under<-carnivores.annual.under$Total
car.ann.count.jump.mod <- lm(car.ann.count.jump ~ 1)
car.ann.count.under.mod <- lm(car.ann.count.under ~ 1)
```

#Annual carnivore count for jumpouts and underpasses separately

```{r, eval=TRUE, echo=FALSE}
dwtest(car.ann.count.jump.mod) #DW test (tests the residuals)-not autocorrelated
dwtest(car.ann.count.under.mod) #not autocorrelated
#also do the Box-Pierce an Ljung-Box tests which test based on the data
Box.test(car.ann.count.jump, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(car.ann.count.under, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(car.ann.count.jump, lag = 1, type = c("Ljung-Box"), fitdf = 0)
Box.test(car.ann.count.under, lag = 1, type = c("Ljung-Box"), fitdf = 0)
acf(car.ann.count.jump, main="", xlab="Total carnivore hourly count for jumpouts") #plot acf
acf(car.ann.count.under, main="", xlab="Total carnivore hourly count for underpasses")
var(car.ann.count.jump)
var(car.ann.count.under)
mean(car.ann.count.jump)
mean(car.ann.count.under)
```

#Monthly carnivore count for jumpouts and underpasses separately

```{r, eval=TRUE, echo=FALSE}
#Monthly carnivore count
car.mon.count.jump<-carnivores.monthly.jump$Total
car.mon.count.under<-carnivores.monthly.under$Total
car.mon.count.jump.mod <- lm(car.mon.count.jump ~ 1)
car.mon.count.under.mod <- lm(car.mon.count.under ~ 1)
dwtest(car.mon.count.jump.mod) #not autocorrelated
dwtest(car.mon.count.under.mod) #not autocorrelated
Box.test(car.mon.count.jump, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(car.mon.count.under, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(car.mon.count.jump, lag = 1, type = c("Ljung-Box"), fitdf = 0)
Box.test(car.mon.count.under, lag = 1, type = c("Ljung-Box"), fitdf = 0)
acf(car.mon.count.jump, main="", xlab="Total carnivore monthly count for jumpouts") 
acf(car.mon.count.under, main="", xlab="Total carnivore monthly count for underpasses")
var(car.mon.count.jump)
var(car.mon.count.under)
mean(car.mon.count.jump)
mean(car.mon.count.under)
```

#Hourly carnivore count for jumpouts and underpasses separately

```{r, eval=TRUE, echo=FALSE}
#Hourly carnivore count
car.hou.count.jump<-carnivores.hourly.jump$Total
car.hou.count.under<-carnivores.hourly.under$Total
car.hou.count.jump.mod <- lm(car.hou.count.jump ~ 1)
car.hou.count.under.mod <- lm(car.hou.count.under ~ 1)
dwtest(car.hou.count.jump.mod) #not autocorrelated
dwtest(car.hou.count.under.mod) #underpass data autocorrelated
Box.test(car.hou.count.jump, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(car.hou.count.under, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(car.hou.count.jump, lag = 1, type = c("Ljung-Box"), fitdf = 0)
Box.test(car.hou.count.under, lag = 1, type = c("Ljung-Box"), fitdf = 0)
acf(car.hou.count.jump, main="", xlab="Total carnivore hourly count for jumpouts") 
acf(car.hou.count.under, main="", xlab="Total carnivore hourly count for underpasses")
var(car.hou.count.jump)
var(car.hou.count.under)
mean(car.hou.count.jump)
mean(car.hou.count.under)
```

#Annual ungulate count for jumpouts and underpasses separately

```{r, eval=TRUE, echo=FALSE}
#Annual ungulate count
ung.ann.count.jump<-ungulates.annual.jump$Total
ung.ann.count.under<-ungulates.annual.under$Total
ung.ann.count.jump.mod <- lm(ung.ann.count.jump ~ 1)
ung.ann.count.under.mod <- lm(ung.ann.count.under ~ 1)
dwtest(ung.ann.count.jump.mod) #not autocorrelated
dwtest(ung.ann.count.under.mod) #not autocorrelated
Box.test(ung.ann.count.jump, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(ung.ann.count.under, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(ung.ann.count.jump, lag = 1, type = c("Ljung-Box"), fitdf = 0)
Box.test(ung.ann.count.under, lag = 1, type = c("Ljung-Box"), fitdf = 0)
acf(ung.ann.count.jump, main="", xlab="Total ungulate annual count for jumpouts") 
acf(ung.ann.count.under, main="", xlab="Total ungulate annual count for underpasses")
var(ung.ann.count.jump)
var(ung.ann.count.under)
mean(ung.ann.count.jump)
mean(ung.ann.count.under)
```

#Monthly ungulate count for jumpouts and underpasses separately

```{r, eval=TRUE, echo=FALSE}
#Monthly ungulate count
ung.mon.count.jump<-ungulates.monthly.jump$Total
ung.mon.count.under<-ungulates.monthly.under$Total
ung.mon.count.jump.mod<- lm(ung.mon.count.jump ~ 1)
ung.mon.count.under.mod <- lm(ung.mon.count.under ~ 1)
dwtest(ung.mon.count.jump.mod) #not autocorrelated
dwtest(ung.mon.count.under.mod) #not autocorrelated
Box.test(ung.mon.count.jump, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(ung.mon.count.under, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(ung.mon.count.jump, lag = 1, type = c("Ljung-Box"), fitdf = 0)
Box.test(ung.mon.count.under, lag = 1, type = c("Ljung-Box"), fitdf = 0)
acf(ung.mon.count.jump, main="", xlab="Total ungulate monthly count for jumpouts")
acf(ung.mon.count.under, main="", xlab="Total ungulate monthly count for underpasses")
var(ung.mon.count.jump)
var(ung.mon.count.under)
mean(ung.mon.count.jump)
mean(ung.mon.count.under)
```

#Hourly ungulate count for jumpouts and underpasses separately

```{r, eval=TRUE, echo=FALSE}
#Hourly ungulate count
ung.hou.count.jump<-ungulates.hourly.jump$Total
ung.hou.count.under<-ungulates.hourly.under$Total
ung.hou.count.jump.mod<- lm(ung.hou.count.jump ~ 1)
ung.hou.count.under.mod <- lm(ung.hou.count.under ~ 1)
dwtest(ung.hou.count.jump.mod) #not autocorrelated
dwtest(ung.hou.count.under.mod) #not autocorrelated
Box.test(ung.hou.count.jump, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(ung.hou.count.under, lag = 1, type = c("Box-Pierce"), fitdf = 0)
Box.test(ung.hou.count.jump, lag = 1, type = c("Ljung-Box"), fitdf = 0)
Box.test(ung.hou.count.under, lag = 1, type = c("Ljung-Box"), fitdf = 0)
acf(ung.hou.count.jump, main="", xlab="Total ungulate hourly count for jumpouts")
acf(ung.hou.count.under, main="", xlab="Total ungulate hourly count for underpasses")
var(ung.hou.count.jump)
var(ung.hou.count.under)
mean(ung.hou.count.jump)
mean(ung.hou.count.under)
```

#-----------------------------Violin plots--------------------------------

```{r, echo=FALSE}
car.ann.count<-carnivores.annual$Total
ung.ann.count<-ungulates.annual$Total
car.mon.count<-carnivores.monthly$Total
ung.mon.count<-ungulates.monthly$Total
car.hou.count<-carnivores.hourly$Total
ung.hou.count<-ungulates.hourly$Total
```

```{r, eval=TRUE, echo=FALSE}
annual.counts<-cbind(car.ann.count,ung.ann.count)
month.counts<-cbind(car.mon.count,ung.mon.count)
#Make the hour counts the same length by adding NAs to carnivore vector
n<-max(length(car.hou.count),length(ung.hou.count))
length(car.hou.count)<-n
hour.counts<-cbind(car.hou.count,ung.hou.count)

vioplot(annual.counts)
vioplot(month.counts)
vioplot(hour.counts)
```

#-----------------Look at whether there is circularity in the dataset--------------------

```{r, echo=FALSE}
#Setup the data differently, get frequencies of count for hour/month/year
newdata<-read.csv("/Users/hannahedwards/Documents/Alberta Parks/Crossing-structures/data/newdata.csv")
#Split by species and then crossing structure
ungulates.under<-subset(newdata, newdata$Species.grouped == "Ungulates" &
                                 newdata$Underpass.type == "Underpass")
ungulates.jump<-subset(newdata, newdata$Species.grouped == "Ungulates" &
                                 newdata$Underpass.type == "Jumpout")
carnivores.under<-subset(newdata, newdata$Species.grouped == "Carnivores" &
                                 newdata$Underpass.type == "Underpass")
carnivores.jump<-subset(newdata, newdata$Species.grouped == "Carnivores" &
                          newdata$Underpass.type == "Jumpout")
```

```{r, eval=TRUE, echo=FALSE}
#Make data circular with hourending
#Vector
unghour<-ungulates.under$HourEnding
carhour<-carnivores.under$HourEnding
unghourc <- circular(unghour, units="hours", template="clock24")
carhourc <- circular(carhour, units="hours", template="clock24")
#the radius of a segment is taken to be the square root of the relative frequency
```
```{r, echo=FALSE, fig.show='hide'}
plot(unghourc)
```
```{r, eval=TRUE, echo=FALSE}
a<-rose.diag(unghourc, bins=24, col="darkgrey", cex=1.5, prop=1.3, add=FALSE,
             xlab="Ungulate hour frequency")
```
```{r, echo=FALSE, fig.show='hide'}
plot(carhourc)
```
```{r, eval=TRUE, echo=FALSE}
b<-rose.diag(carhourc, bins=24, col="darkgrey", cex=1.5, prop=1.3, add=FALSE,
             xlab="Carnivore hour frequency")
```

```{r, eval=TRUE, echo=FALSE}
#Make data circular with Month
#Vector
ungmon<-ungulates.under$Month
carmon<-carnivores.under$Month
ungmonc <- circular(ungmon, units="hours", template="clock12")
carmonc <- circular(carmon, units="hours", template="clock12")
#the radius of a segment is taken to be the square root of the relative frequency
```
```{r, echo=FALSE, fig.show='hide'}
plot(ungmonc)
```
```{r, eval=TRUE, echo=FALSE}
c<-rose.diag(ungmonc, bins=12, col="darkgrey", cex=1.5, prop=1.3, add=FALSE,
             xlab="Ungulate month frequency")
```
```{r, echo=FALSE, fig.show='hide'}
plot(carmonc)
```
```{r, eval=TRUE, echo=FALSE}
d<-rose.diag(carmonc, bins=12, col="darkgrey", cex=1.5, prop=1.3, add=FALSE,
             xlab="Carnivore month frequency")
```